---
title: "Thesis5.0"
author: "Hirsch"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stargazer)
library(ggplot2)
library(devtools)
library(ggthemes)
library(plm)
library(dplyr)
library(scales)
library(tidyverse)
```

The goal of Thesis 5.0 Script is to take my data panel and code observations into categories.

Office Buildings built before 2009 that as of 2023 are coded as:

 1. Office Space still Office Space
 2. Office Space converted into Residential
 3. Office Space converted into Other Space
 4. Office Space converted into Hotel Space
 5. Office Space converted into Retail Space
 6. Office Space converted into Mixed Use Space
 7. Office Space converted into Vacant Land <- to be clear "Vacant" explicitly means vacant land
 
 When Office Buildings were converted to Residential:
 
 1. Adaptive Reuse <- Construction year did not change
 2. Demolish & Rebuilt <- Construction year changed
 
MAIN Q: HOW MANY OFFICE TO RESIDENTIAL CONVERSIONS ARE ADAPTIVE REUSE VS DEMOLISH & REBUILD
 

 
```{r}
FINALPANEL <- read.csv("~/Desktop/SENIOR THESIS/FINALDATA/FINALPANEL.csv")
head(FINALPANEL)
```

```{r}
#Making the Panel Data Frame a time-series
FINALPANEL <- pdata.frame(FINALPANEL, index = c("BBLE", "Year"))
pvar(FINALPANEL)
```

FINALPANEL currently has offices that were converted from other buildings or new construction - It is all buildings that were offices at any time between 2010-2023

I want a panel that only has buildings that were office buildings in 2010 and complete 14yrs of data

```{r}

#Remove BBLEs that were converted to offices by only selecting those that were offices in 2010

oldoff <- FINALPANEL %>% group_by(BBLE) %>% subset(Year==2010 & BLD_Cat == "Office")

OFFICEPANEL <- FINALPANEL[FINALPANEL$BBLE %in% oldoff$BBLE, ]

uncuttesting <- OFFICEPANEL %>% group_by(BBLE) %>% count()
dim(uncuttesting)
table(uncuttesting$n)

#How many of the 9,072 buildings were offices in 2010?
#6,776 with 6403 with 14 observations

#Remove BBLEs without 14 observations
cnt <- OFFICEPANEL %>% group_by(BBLE) %>% count()
OFFICEPANEL <- OFFICEPANEL[OFFICEPANEL$BBLE %in% cnt[cnt$n == 14, ]$BBLE, ]

cuttesting <- OFFICEPANEL %>% group_by(BBLE) %>% count()
table(cuttesting$n)

#this matches what we expected

#6,403 Observations of 2010 office buildings in 2023
```

```{r}
#Creating Categories of Outcomes: what the building was taxed as in 2023

OFFICEPANEL <- OFFICEPANEL %>% group_by(BBLE) %>%
  mutate(OUTCOME = case_when(
    last(BLD_Cat) == "Res" ~ "Res Conv",
    last(BLD_Cat) == "Office" ~ "Office",
    last(BLD_Cat) == "Hotel" ~ "Hotel Conv",
    last(BLD_Cat) == "Retail" ~ "Retail Conv",
    last(BLD_Cat) == "Vacant" ~ "Vacant Land",
    last(BLD_Cat) == "Other" ~ "Other",
    last(BLD_Cat) == "MixedRes" ~ "MixedRes",
    .default = "Missing"
  )
  )

#Need to explain these categories: especially how Mixed Residential are office buildings that are converted to the S classes, eg. primarily residential, but have retained Office or retail use. Some of these are bigger conversions than others: many of these buildings are small and its just a change in which half of the building is estimated to be generating more revenue. 
```

```{r}

head(OFFICEPANEL)
write.csv(OFFICEPANEL, "~/Desktop/SENIOR THESIS/FINALDATA/OFFICEPANEL.csv")

OFFICEPANEL <- read.csv("~/Desktop/SENIOR THESIS/FINALDATA/OFFICEPANEL.csv")
```



```{r}
#I think what I'm actually curious about here is how many new units were created, not the building classes themselves.
#How many new units were created in each borough out of office buildings?

OFFICEPANEL <- OFFICEPANEL %>% group_by(BBLE) %>%
  mutate(NewUnits = last(ResUnits) - first(ResUnits))

NEWUNITS23 <- OFFICEPANEL %>% filter(Year == 2023) %>% subset(OUTCOME == "Res Conv" | OUTCOME == "MixedRes")

NewUnitTable <- NEWUNITS23 %>% group_by(BORO, OUTCOME) %>% summarise(Sum_Units = sum(NewUnits), .groups = 'drop')

NewUnitTable <- NewUnitTable %>% mutate(BORO = case_when(
    BORO == 1 ~ "Manhattan",
    BORO == 2 ~ "Bronx",
    BORO == 3 ~ "Brooklyn",
    BORO == 4 ~ "Queens",
    BORO == 5 ~ "Staten Island"))
table(NewUnitTable$BORO)

NewUnitTable <- NewUnitTable %>% mutate(BORO = fct_relevel(BORO, 
            "Manhattan", "Bronx", "Brooklyn", 
            "Queens", "Staten Island"))

ggplot(NewUnitTable, aes(BORO, Sum_Units, fill = OUTCOME)) +
  geom_col(position = "dodge") +
  labs(title = 'Additional Residential Units From Conversion to Residential vs Mixed-Use', subtitle = "2010-2023 in NYC", x = 'Borough', y = 'New Units Created', fill = 'Method of Conversion', caption = "Data from NYC DOF and NYC DOB 2023") + 
    theme_few() + 
  theme(text = element_text(size = 10), plot.caption.position = "plot") + 
  scale_fill_manual(values = c("coral2","grey"), labels = c("Mixed-Use Residential Conversion", "Residential Conversion"))

#Great so I can just focus on the clean "Residential" conversions, because all the messy mixed use conversions tend to create relatively few units. Looking at the classes 'A0','L1','A1','L2','A2','L3','A3','L8','A4','L9','A5','A6','R1','A7','R2','A8','R3','A9','R4','A10','A11','R6','A12','R7','A13','R8','A14','R9','A15','A16','S0','A17','S1','A18','S2','A19','S3','A20','S4','A21','S5','A22','S9','A23','A24','A25','A26','A27','D0','D1','D2','D3','D4','D5','D6','D7','D8','D9','DB','DC'

```

```{r}
subsetted1 <- OFFICEPANEL %>% subset(OUTCOME == "Res Conv" & Year == 2023)
sum(subsetted1$NewUnits)
```
8759 New Units created between 2010-2023 via conversion to Residential to Office Building

```{r}
write.csv(OFFICEPANEL, "~/Desktop/SENIOR THESIS/FINALDATA/OFFICEPANEL.csv")

OFFICEPANEL <- read.csv("~/Desktop/SENIOR THESIS/FINALDATA/OFFICEPANEL.csv")
```


```{r}
#Just in 2023 for simple graphing
OFFICES23 <- OFFICEPANEL %>% subset(Year == "2023")
```

```{r, fig.align='center'}

ggplot(data = OFFICES23, aes(x = factor(OUTCOME), 
                          y = prop.table(stat(count)), 
                          fill = factor(OUTCOME), 
                          label = scales::percent(prop.table(stat(count))))) +
    geom_bar(position = "dodge") + 
    geom_text(stat = 'count',
              position = position_dodge(.9), 
              vjust = -0.5, 
              size = 3) + 
      scale_y_continuous(labels = scales::percent) +
      scale_x_discrete(guide = guide_axis(angle = 45)) +
      labs(title = 'What happened to 2010 Office Properties?', subtitle = "Conversion Rate on 6,403 Buildings",x = "Property Category in 2023", y = 'Proportion', fill = 'Building Class Category in 2023', caption = "Data from New York City Department of Finance Property Tax Rolls 2009-2023") + 
      theme_classic() + 
      theme(text = element_text(size = 10), legend.position = "right", plot.caption.position = "plot") + 
      scale_fill_colorblind(labels = c("Hotel Conversion","Mixed-Use Residential", "No Conversion - Office Building", "Other Conversion", "Residential Conversion", "Retail Conversion", "Vacant - Office Demolished"))


```
NOTE: make this as a Sankey plot in Tableu with OFFICEPANEL !!!

How about conversions just in Manhattan, where there is the least available amount of new land?

```{r}
#subset for just manhattan
MOFFICES23 <- OFFICES23 %>% subset(BORO == 1)

MOFFICES23 %>% group_by(BBLE) %>% dim()
```


```{r}
ggplot(data = MOFFICES23, aes(x = factor(OUTCOME), 
                          y = prop.table(stat(count)), 
                          fill = factor(OUTCOME), 
                          label = scales::percent(prop.table(stat(count))))) +
    geom_bar(position = "dodge") + 
    geom_text(stat = 'count',
              position = position_dodge(.9), 
              vjust = -0.5, 
              size = 3) + 
      scale_y_continuous(labels = scales::percent) +
      scale_x_discrete(guide = guide_axis(angle = 45)) +
      labs(title = '2010 Office Properties in Manhattan', subtitle = "Conversion Rate on 1,936 buildings", x = "Property Category in 2023", y = 'Proportion', fill = 'Building Class Category in 2023' , caption = "Data from New York City Department of Finance Property Tax Rolls 2009-2023") + 
      theme(text = element_text(size = 10), legend.position = "right", plot.caption.position = "plot") + 
      theme_classic() + 
      scale_fill_colorblind(labels = c("Hotel Conversion","Mixed-Use Residential", "No Conversion - Office Building", "Other Conversion", "Residential Conversion", "Retail Conversion", "Vacant - Office Demolished"))
```


```{r}
table(MOFFICES23$OUTCOME)
```


```{r}
#Let's break down Retail Conversions in Manhattan

MRETAIL23 <- subset(MOFFICES23, OUTCOME == "Retail Conv")

ggplot(data = MRETAIL23, aes(x = factor(BLD_Class), 
                          fill = factor(BLD_Class))) +
    geom_bar(position = "dodge") + 
  geom_text(stat='count', aes(label=after_stat(count)), vjust=2, size = 4, color = "white") +
    labs(title = 'Retail Conversions in Manhattan', subtitle = "Building class of 84 converted buildings", x = 'Office to Retail Conversion Class', y = 'Count', fill = 'Retail Class Category in 2023', caption = "Data from NYC DOF and NYC DOB 2023") + 
    theme_classic() + 
  theme(text = element_text(size = 10), plot.caption.position = "plot") + 
  scale_fill_colorblind(labels = c("K1 - One Story Retail Building", "K2 - Multi-Story Retail Building", "K4 - Predominant Retail With Other Uses", "K7 - Banking Facilities With or Without Parking"))

```


```{r}
#Let's break down Retail Conversions in Brooklyn

BKOFFICES23 <- OFFICES23 %>% subset(BORO == 3)

BKOFFICES23 %>% group_by(BBLE) %>% dim()

BKRETAIL23 <- subset(BKOFFICES23, OUTCOME == "Retail Conv")

ggplot(data = BKRETAIL23, aes(x = factor(BLD_Class), 
                          fill = factor(BLD_Class))) +
    geom_bar(position = "dodge") + 
  geom_text(stat='count', aes(label=after_stat(count)), vjust=-0.25, size = 4, color = "black") +
    labs(title = 'Retail Conversions in Brooklyn', subtitle = "Building class of 84 converted buildings", x = 'Office to Retail Conversion Class', y = 'Count', fill = 'Retail Class Category in 2023', caption = "Data from NYC DOF and NYC DOB 2023") + 
    theme_classic() + 
  theme(text = element_text(size = 10), plot.caption.position = "plot") + 
  scale_fill_colorblind(labels = c("K1 - One Story Retail Building", "K2 - Multi-Story Retail Building", "K4 - Predominant Retail With Other Uses", "K5 - STAND-ALONE FOOD ESTABLISHMENT", "K7 - Banking Facilities With or Without Parking", "K9 - MISCELLANEOUS STORE BUILDING"))


```


```{r}
#Office to Residential Conversions by Boro

ALLRES23 <- subset(OFFICES23, OUTCOME == "Res Conv")

ALLRES23 <- ALLRES23 %>% mutate(BORO = case_when(
    BORO == 1 ~ "Manhattan",
    BORO == 2 ~ "Bronx",
    BORO == 3 ~ "Brooklyn",
    BORO == 4 ~ "Queens",
    BORO == 5 ~ "Staten Island"))

ALLRES23 <- ALLRES23 %>% mutate(BORO = fct_relevel(BORO, 
            "Manhattan", "Bronx", "Brooklyn", 
            "Queens", "Staten Island"))

ggplot(data = ALLRES23, aes(x = factor(BORO), 
                          fill = factor(BORO))) +
    geom_bar(position = "dodge") + 
  geom_text(stat='count', aes(label=after_stat(count)), vjust=2, size = 4, color = "white") +
    labs(title = 'Office to Residential Building Conversions in NYC', subtitle = "", x = 'Borough', y = 'Count', fill = 'Borough', caption = "Data from NYC DOF and NYC DOB 2023") + 
    theme_classic() + 
  theme(text = element_text(size = 10), plot.caption.position = "plot") + 
  scale_fill_colorblind(labels = c("Manhattan", "Bronx", "Brooklyn", "Queens", "Staten Island"))



```


```{r}
#Office to Mixed Residential Conversions by Boro

MIXEDRES23 <- subset(OFFICES23, OUTCOME == "MixedRes")

MIXEDRES23 <- MIXEDRES23 %>% mutate(BORO = case_when(
    BORO == 1 ~ "Manhattan",
    BORO == 2 ~ "Bronx",
    BORO == 3 ~ "Brooklyn",
    BORO == 4 ~ "Queens",
    BORO == 5 ~ "Staten Island"))

MIXEDRES23 <- MIXEDRES23 %>% mutate(BORO = fct_relevel(BORO, 
            "Manhattan", "Bronx", "Brooklyn", 
            "Queens", "Staten Island"))

ggplot(data = MIXEDRES23, aes(x = factor(BORO),
                          fill = factor(BLD_Class))) +
    geom_bar(position = "dodge") + 
    labs(title = 'Office to Mixed Residential Use Conversions in NYC', subtitle = "Have mixed-use conversions created new housing?", x = 'Borough', y = 'Count', fill = 'Mixed Residential Class in 2023', caption = "Data from NYC DOF and NYC DOB 2023") + 
    theme_classic() + 
  theme(text = element_text(size = 10), plot.caption.position = "plot") + 
  scale_fill_colorblind(labels = c("S1 - PRIMARILY 1 FAMILY WITH 1 STORE OR OFFICE", "S2 - PRIMARILY 2 FAMILY WITH 1 STORE OR OFFICE", "S3 - PRIMARILY 3 FAMILY WITH 1 STORE OR OFFICE", "S4 - PRIMARILY 4 FAMILY WITH 1 STORE OROFFICE", "S5 - PRIMARILY 5-6 FAMILY WITH 1 STORE OR OFFICE", "S9 - SINGLE OR MULTIPLE DWELLING WITH STORES OR OFFICES"))
```



```{r}
#Are the Brooklyn S2 buildings actually conversions in use, or just changing in coding
BKMRTEST <- subset(OFFICEPANEL, BORO == 3 & BLD_Class == "S2")

Test2010 <- subset(OFFICEPANEL, Year == 2010)

BKMRTEST_Table <- Test2010[Test2010$BBLE %in% BKMRTEST$BBLE, ]



ggplot(data = BKMRTEST_Table, aes(x = factor(BLD_Class),
                          fill = factor(BLD_Class))) +
    geom_bar(position = "dodge") + 
    labs(title = 'Conversions to Mixed 2 Family Class in Brooklyn', subtitle = "Do S2 class conversions in Brooklyn actually represent a singificant change in use? ", x = 'Original Office Class', y = 'Count', fill = 'Original Office Class in 2010', caption = "Data from NYC DOF and NYC DOB 2023") + 
    theme_classic() + 
  theme(text = element_text(size = 10), plot.caption.position = "plot") + 
  scale_fill_colorblind(labels = c("O5 - OFFICE WITH COMM - 1 TO 6 STORIES", "O7 - PROFESSIONAL BUILDINGS/STAND ALONE FUNERAL HOMES", "O8 - OFFICE WITH APARTMENTS ONLY (NO COMM)", "O9 - MISCELLANEOUS AND OLD STYLE BANK BLDGS."))
```



Now Graph classes of Residential Conversions in Manhattan:

```{r}
MRES23 <- subset(MOFFICES23, OUTCOME == "Res Conv")

table(MRES23$BLD_Class)

MRES23 <- MRES23 %>%
  mutate(Class_Simplified = case_when(
    BLD_Class == "D1" | BLD_Class == "D3"| BLD_Class == "D5" | BLD_Class == "D6"| BLD_Class == "D7" | BLD_Class == "D8" | BLD_Class == "D9" | BLD_Class == "D6" ~ "D1:D9",
    .default = BLD_Class))

ggplot(data = MRES23, aes(x = factor(Class_Simplified), 
                          fill = factor(Class_Simplified))) +
    geom_bar(position = "dodge") + 
  geom_text(stat='count', aes(label=after_stat(count)), vjust=-0.25, size = 4, color = "black") +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
    labs(title = '2010-2023 Residential Conversions in Manhattan', subtitle = "Building class of 55 converted buildings", x = 'Office to Residential Conversion Class', y = 'Count', fill = 'Residential Class Category in 2023', caption = "Data from NYC DOF and NYC DOB 2023") + 
    theme_classic() + 
  theme(text = element_text(size = 10), plot.caption.position = "plot") + scale_fill_ordinal(labels = c("A4 - CITY RESIDENCE ONE FAMILY", "A5 - ONE FAMILY ATTACHED OR SEMI-DETACHED", "A7 - MANSION TYPE OR TOWN HOUSE", "B1 - TWO FAMILY BRICK", "C0 - THREE FAMILIES", "C3 - FOUR FAMILIES", "C7 - WALK-UP APT. OVER SIX FAMILIES WITH STORES","ELEVATOR APT (D1,D3,D5,D6,D7,D8,D9)"))

```

```{r}
BKRES23 <- subset(OFFICES23, OUTCOME == "Res Conv" & BORO == 3)


BKRES23 <- BKRES23 %>%
  mutate(Class_Simplified = case_when(
    BLD_Class == "D1" | BLD_Class == "D3"| BLD_Class == "D5" | BLD_Class == "D6"| BLD_Class == "D7" | BLD_Class == "D8" | BLD_Class == "D9" | BLD_Class == "D6" ~ "D1:D9",
    BLD_Class == "B1" | BLD_Class == "B2"| BLD_Class == "B3" ~ "B1,B2,B3",
    .default = BLD_Class))

ggplot(data = BKRES23, aes(x = factor(Class_Simplified), 
                          fill = factor(Class_Simplified))) +
    geom_bar(position = "dodge") + 
  geom_text(stat='count', aes(label=after_stat(count)), vjust=-0.25, size = 4, color = "black") +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
    labs(title = 'Office to Residential Conversions in Brooklyn (2010-2023)', subtitle = "Building class of 56 converted buildings", x = 'Office to Residential Conversion Class', y = 'Count', fill = 'Residential Class Category in 2023', caption = "Data from NYC DOF and NYC DOB 2023") + 
    theme_classic() + 
  theme(text = element_text(size = 10), plot.caption.position = "plot") + scale_fill_ordinal(labels = c("A1 - TWO STORIES DETACHED SM OR MID","A3 - LARGE SUBURBAN RESIDENCE",  "A4 - CITY RESIDENCE ONE FAMILY", "A5 - ONE FAMILY ATTACHED OR SEMI-DETACHED", "TWO FAMILY BRICK (B1,B2, B3)", "C0 - THREE FAMILIES","C1 - OVER SIX FAMILIES WITHOUT STORES","C2 - FIVE TO SIX FAMILIES","C3 - FOUR FAMILIES", "C7 - WALK-UP APT. OVER SIX FAMILIES WITH STORES","ELEVATOR APT (D1,D3,D5,D6,D7,D9)"))


```

