---
title: "Thesis6.1"
author: "Hirsch"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(patchwork)
library("Hmisc")
library(corrplot)
```

```{r}
OFFICEPANELCLEAN <- read.csv("~/Desktop/SENIOR THESIS/FINALDATA/RESIDENTIALCONVERSIONSPANEL.csv")
```
#When i stopped here I was on the song "Opal"

#tomorrow: I either run a regression for Office buildings: Xs are in my data and Y is conversion... compare coeeficients for New Construction vs. Reuse? Could also do a Probit model? not that interested in what makes a building a good condidate for conversion vs. New Construction: private developers will figure that out and its obvious empirically that it will be some split between the two.


#Could also do a machine learning tree model with variables: can I predict whether a building will be converted via new construction or reuse? is there overlap between the two or are they totally different types of buildings?



```{r}

panel <- OFFICEPANELCLEAN[,-1]
panel

```
```{r}
Conversions <- filter(panel, OUTCOME == "Res Conv")

Conversions <- Conversions %>% group_by(BBLE) %>%
  mutate(BLD_Story_2010 = first(BLD_Story))

Conversions <- Conversions %>% group_by(BBLE) %>%
  mutate(OG_Year_Built_2010 = first(Year_Built))

Conversions <- Conversions %>% group_by(BBLE) %>%
  mutate(Zoning_2010 = first(ZONING))

Conversions <- Conversions %>% group_by(BBLE) %>%
  mutate(FinMktTot_2010 = first(FinMktTot))

Conversions <- Conversions %>% group_by(BBLE) %>%
  mutate(BLD_Class_2010 = first(BLD_Class))

Conversions <- Conversions %>% group_by(BBLE) %>%
  mutate(Gross_SQFT_2010 = first(Gross_SQFT))


#If 2023 FinMktTotal value is missing, use 2022 Values
Conversions <- Conversions %>% group_by(BBLE) %>%
  mutate(FinMktTot = case_when(
    FinMktTot != 0 ~ FinMktTot,
    FinMktTot == 0 ~ nth(FinMktTot,13),
    .default = NA,
  ))

#This is the outcome variable - value per unit
Conversions <- Conversions %>% group_by(BBLE) %>%
  mutate(PerResUnit = FinMktTot/ResUnits)

Conversions <- Conversions %>% group_by(BBLE) %>%
  mutate(OfficePerSQFT_2010 = FinMktTot_2010/Gross_SQFT_2010)

Conversions <- Conversions %>% group_by(BBLE) %>%
  mutate(PerSQFT_2023 = FinMktTot/Gross_SQFT)

Conversions <- filter(Conversions, Year == 2023)


Conversions <- Conversions %>% group_by(BBLE) %>%
  mutate(CORNER = case_when(
    CORNER == "CR" | CORNER == "NE"| CORNER == "NW"| CORNER == "SE"| CORNER == "SW" ~ 1,
    .default = 0,
  )
  )

Conversions <- Conversions %>% group_by(BBLE) %>%
  mutate(Delta = FinMktTot - FinMktTot_2010)

#Need outcome Variable to be Numeric
#Conversions <- Conversions %>% group_by(BBLE) %>%
#  mutate(Conv_Method = case_when(
#    Conv_Method == "New Construction" ~ 0,
#    Conv_Method == "Reuse" ~ 1,
#    .default = NA,
#  )
 # )
Conversions$Conv_Method <- as.factor(Conversions$Conv_Method)

Conversions
```

```{r}
summary(Conversions$PerSQFT_2023)
```


```{r}
model1 <- lm(log(PerResUnit) ~ Conv_Method, data = Conversions)

#model1 <- lm(Conv_Method ~ OG_Year_Built_2010 + BORO + ZONING + CORNER + BLD_Story_2010 + OG_Year_Built_2010 + Zoning_2010 + FinMktTot_2010 + BLD_Class_2010 + Gross_SQFT_2010, data = Conversions)

model1
```

```{r}
exp(1.441) #A building being reused is associated with a 322% increase in cost per unit. 
```

```{r}
plot1 <- plot(x = Conversions$Conv_Method,
     y = log(Conversions$PerResUnit),
     main = "Scatterplot Conversions method and Value Per Residential Unit",
     xlab = "Redeveloped (0) or Reused (1)",
     ylab = "Log Value per Unit",
     pch = 20,
     ylim = c(5, 20),
     cex.main = 0.8)

# add the estimated regression line
abline(model1, 
       lwd = 1.8, 
       col = "steelblue")

#add violin chart
```
```{r}
graph1 <- ggplot(Conversions, aes(x=Conv_Method, y=log(Conversions$PerResUnit), fill = Conv_Method)) + # fill=name allow to automatically dedicate a color for each group
  geom_violin() + 
  labs(x = "", y = 'Value per Residential Unit (Log)', fill = 'Conversion Method') + theme_few() +
  theme(panel.background = element_rect(fill = "white", colour = "gray50"), 
        axis.text.x = element_text(size = 15), 
        axis.text.y = element_text(size = 12),
       panel.grid.major.y = element_line(colour = "gray80"),
       legend.position = "none", aspect.ratio = 1.1
       ) + 
  geom_boxplot(width=0.3, color="gray30", alpha=0.2) + scale_fill_manual(values = c("grey","lightgreen")) + stat_summary(fun="median", geom="text", aes(label=round(after_stat(y), digits = 2)), vjust=-2, position = position_nudge(x = 0.27, y = -0.9))

graph1

```

```{r}
graph2 <- ggplot(Conversions, aes(x=Conv_Method, y=log(Conversions$PerSQFT_2023), fill = Conv_Method)) + # fill=name allow to automatically dedicate a color for each group
  geom_violin() + 
  labs(x = "", y = 'Value per SQFT (Log)', fill = 'Conversion Method') + theme_few() +
  theme(panel.background = element_rect(fill = "white", colour = "gray50"), 
        axis.text.x = element_text(size = 15), 
        axis.text.y = element_text(size = 12),
       panel.grid.major.y = element_line(colour = "gray80"),
       legend.position = "none", aspect.ratio = 1.1
       ) + 
  geom_boxplot(width=0.3, color="gray30", alpha=0.2) + scale_fill_manual(values = c("grey","lightgreen")) + stat_summary(fun="median", geom="text", aes(label=round(after_stat(y), digits = 2)), vjust=-2, position = position_nudge(x = 0.27, y = -0.35))

graph2
```


```{r}

#lets try to transform building value?

density1 <- Conversions %>%
  ggplot(aes(x=log(FinMktTot), group = Conv_Method, fill=Conv_Method)) +
    geom_density(adjust=1, alpha=.4) +
  theme(legend.position = "right") + scale_fill_manual(values = c("grey","lightgreen"))

density2 <- Conversions %>%
  ggplot(aes(x= log(PerResUnit), group = Conv_Method, fill=Conv_Method)) +
    geom_density(adjust=1, alpha=.4) +
  theme(legend.position = "right")+ scale_fill_manual(values = c("grey","lightgreen"))

density3 <- Conversions %>%
  ggplot(aes(x= log(PerSQFT_2023), group = Conv_Method, fill=Conv_Method)) +
    geom_density(adjust=1, alpha=.4) +
  theme(legend.position = "right")+ scale_fill_manual(values = c("grey","lightgreen"))


density1 + plot_annotation(title = "Data Density - Market Value")
density2 + plot_annotation(title = "Data Density - Per Unit")
density3 + plot_annotation(title = "Data Density - Per SQFT")
```

```{r}
summary(log(Conversions$PerResUnit))
summary(Conversions$FinMktTot)

PerUnitShap <- shapiro.test(log(Conversions$PerResUnit)) # because the p value < 0.5 it is statistically different from a normal distribution
FinMktTotShap <- shapiro.test(log(Conversions$FinMktTot)) # because the p value < 0.5 it is statistically different from a normal distribution
PerSQFTShap <- shapiro.test(log(Conversions$PerSQFT_2023)) # because the p value < 0.5 it is statistically different from a normal distribution


PerUnitShap

FinMktTotShap
PerSQFTShap

shaplist <- list(PerUnitShap, FinMktTotShap, PerSQFTShap)

summary(PerUnitShap)


```

```{r}
PerResmodel1 <- lm(log(PerResUnit) ~ Conv_Method, data = Conversions)
summary(model1)

plot(model1)

#Beta: 1.44 ***
```
```{r}
model2 <- lm(log(PerSQFT_2023) ~ Conv_Method, data = Conversions)
summary(model2)

plot(model2)
```

```{r}
#Correlation Matrix, no factor or loft, too many NAs

my_data <- Conversions[, c("Conv_Method","CORNER","HOTEL_AREA_GROSS","OFFICE_AREA_GROSS","RETAIL_AREA_GROSS", "TotalUnits", "Delta","FinMktTot_2010","FinMktTot", "PerResUnit", "PerSQFT_2023")]

my_data$Conv_Method <- as.numeric(my_data$Conv_Method)


summary(my_data)

simple_cor <- cor(my_data)
#round(simple_cor, 2)

#Conv_Method <- Total Units, Delta, Retail, is sig correlated and Per Res Unit
#Corner <- Retail, Total Units, FinMktTot, FinMktTot_2010
#Hotel Area <- Total Units, Delta, FinMktTot_2010, FinMktTot
#Office Area <- Delta
#Retail strongly correlated with Everything
#Loft NAs
#Factory NA
#Total Units <- Conv_Method, CORNER, Delta, FinMktTot, FinMktTot_2010, Retail Hotel Area
#Delta <- Conv_Method, CORNER, FinMktTot, FinMktTot_2010, Retail Hotel Area, Total Units
#FinMktTot_2010 <- everything except office and conversion method
#FinMktTot <- everything except office and conversion method or Per Res Unit

#Per Res Unit <- correlated with Conv_Method, Delta, and FinMktTot


cor2 <- rcorr(as.matrix(my_data))
#cor2

```

```{r}
cor2$P <- cor2$P %>% replace(is.na(.), 1)

correlationmatrix <- corrplot(cor2$r, type="upper", order="hclust", 
         p.mat = cor2$P, sig.level = 0.05, insig = "blank")
```


```{r}
#Correlation Matrix but with log


my_data2 <- Conversions[, c("Conv_Method","CORNER","HOTEL_AREA_GROSS","OFFICE_AREA_GROSS","RETAIL_AREA_GROSS", "TotalUnits", "Delta","FinMktTot_2010","FinMktTot", "PerResUnit", "PerSQFT_2023", "BORO", "OfficePerSQFT_2010")]

my_data2$Conv_Method <- as.numeric(my_data$Conv_Method)

my_data2$FinMktTot_2010 <- log(my_data2$FinMktTot_2010)
my_data2$FinMktTot <- log(my_data2$FinMktTot)
my_data2$PerResUnit <- log(my_data2$PerResUnit)
my_data2$BORO <- as.factor(my_data2$BORO)

my_data2 <- dummy_cols(my_data2, remove_first_dummy = FALSE)
newnames <- dummy_cols(my_data2, remove_first_dummy = FALSE, return_generated_variables = TRUE)

#my_data2$BORO_Bronx <- as.numeric(mydata2$BORO_Bronx)

my_data2$BORO <- NULL

my_data2

simplecor2 <- cor(my_data2)
round(simplecor2, 2)

#Conv_Method <- Total Units, Delta, Retail, is sig correlated - Per Res Unit
#Corner <- Retail, Total Units, FinMktTot, FinMktTot_2010
#Hotel Area <- Total Units, Delta, FinMktTot_2010, FinMktTot
#Office Area <- Delta
#Retail strongly correlated with Everything
#Loft NAs
#Factory NA
#Total Units <- Conv_Method, CORNER, Delta, FinMktTot, FinMktTot_2010, Retail Hotel Area
#Delta <- Conv_Method, CORNER, FinMktTot, FinMktTot_2010, Retail Hotel Area, Total Units
#FinMktTot_2010 <- everything except office and conversion method
#FinMktTot <- everything except office and conversion method - Per Res Unit

#Per Res Unit <- correlated with Conv_Method and FinMktTot


corrplot2 <- rcorr(as.matrix(my_data2))
```

```{r}
corrplot2$P <- corrplot2$P %>% replace(is.na(.), 0)

correlationmatrix2 <- corrplot(corrplot2$r, type = "upper", order="hclust", 
         p.mat = corrplot2$P, sig.level = 0.05, insig = "blank", tl.col = "black", tl.cex = 0.8)
```
```{r}
#We want everything that might correlate with Mkt, Per Res Unit or Per SQFT (outcome), but won't correlate with Conv_Method (independent var)

#FinMkt: Boro, Fin2010, Hotel, retail, totalunits, delta, corner, Conv_method, SQFT2010
#PerResUnit: BORO_manhattan, FinMKt, Retail area, Total units, Delta, SQFT2010
#Conv_Method: FinMkt2010, FInmkt, retail area, total units, delta
#PerSQFT: Boro, finmkttot, retail, total, delta, boro, conv_method, PerResUnit, SQFT2010

#Non-multi-collinear controls for MktTot: BORO, Corner, SQFT2010

#Non-multi-collinear controls for PerResUnit: BORO, SQFT2010

#Non-multi-collinear controls for per sqft: BORO, SQFT2010

#There's nothing that's not all tangled up in the decision to convert or not.
#Therefore the interpretation of the regression is entirely descriptive: not causal. I can't say that reuse causes the resulting units to be more expensive: but I can say that buildings produced by reuse tend to also have more expensive units.

#It's interesting that FinMkt2010 is significantly correlated with Conv_method, but perSQFT2010 is not. 

#It's also interesting that Conv_Method is not statistically significantly correlated with the Boros, even though the descriptive data shows that manhattan has seen proportionally more adaptive reuse. 
```

```{r}

testmodel1 <- lm(log(FinMktTot_2010) ~ Conv_Method, data = Conversions)
summary(testmodel1) #Conv Method explains 2% of variation in Mkt2010 (neg correlation) #sig

testmodel3 <- lm(log(OfficePerSQFT_2010) ~ Conv_Method, data = Conversions)
summary(testmodel3) #Conv Method explains <1% of variation in OfficePerSQFT_2010. (neg correlations) #notsig

testmodel2 <- lm(log(FinMktTot_2010) ~ Conv_Method + BORO, data = Conversions)
summary(testmodel2) #Conv Method and BORO explains 40% of variation in Mkt2010 (neg correlation) #sig

testmodel4 <- lm(log(OfficePerSQFT_2010) ~ Conv_Method + BORO, data = Conversions)
summary(testmodel4) #Conv Method and BORO explains 25% of variation in OfficePerSQFT_2010. (neg correlations) #notsig

testmodel5 <- lm(log(FinMktTot_2010) ~ BORO, data = Conversions)
summary(testmodel5) #BORO explains 40% of variation in Mkt2010

testmodel6 <- lm(log(OfficePerSQFT_2010) ~ BORO, data = Conversions)
summary(testmodel6) #BORO explains 25% of variation in OfficePerSQFT_2010.
```
In the correlation matrix, one interesting observation is that FinMkt2010 is significantly correlated with Conv_method, but perSQFT2010 is not. This suggests that perSQFT2010 would be a better regressor. To confirm this, I looked at its relationship with their relationship with BORO as well.

By performing the following Regressions and I was also able to confirm that OfficePerSQFT_2010 is less associated with BORO than FinMktTot2010.

$log(FinMktTot2010)_i = \beta_0 + \beta_1 ConversionMethod_i + \beta_2 BORO_i + \epsilon_i$
$log(OfficePerSQFT2010)_i = \beta_0 + \beta_1 ConversionMethod_i + \beta_2 BORO_i + \epsilon_i$

While BORO explains ~40% of the variation in FinMktTot2010, BORO only explains ~25% of the variation in OfficePerSQFT2010. 


While this means both FinMktTot2010 and OfficePerSQFT2010 will be multicollinear with BORO, but FinMktTot_2010 is more multicollinear than OfficePerSQFT_2010. This makes OfficePerSQFT more appropriate for use in a regression than FinMktTot_2010.

Additionally, this makes sense because by looking at SQFT you help account for the fact that I expect buildings in Manhattan to be denser and therefore more per square foot.

```{r}
model1 <- lm(log(PerSQFT_2023) ~ Conv_Method + BORO, data = Conversions)

summary(model1)

plot(model1)
model1
#stargazer(model1)
```

```{r}
model2 <- lm(log(PerSQFT_2023) ~ Conv_Method + BORO + log(OfficePerSQFT_2010), data = Conversions)

summary(model2)

plot(model2)
model2
```
```{r}
model3 <- lm(log(PerSQFT_2023) ~ Conv_Method, data = Conversions)

summary(model3)

plot(model3)
model3
```
```{r}
Conversions

model4 <- lm(log(PerSQFT_2023) ~ Conv_Method + BORO + BLD_Story + Gross_SQFT + Year_Built + OfficePerSQFT_2010, data = Conversions)

summary(model4)

plot(model4)
```


The issue with the multicollinearity is that it means we can't interpret the increase in average value per square foot that we attribute in our model to Conv_Method, is actually attributable to Conv_Method. Because The other components are co-linear they make the bias estimate for the effect of Reuse. 


```{r}
#Another strategy?

#Treatment group: Reuse
#Control group: Conversion

Welch <- t.test(formula = log(PerSQFT_2023) ~ Conv_Method, data = Conversions, var.equal = FALSE )

Welch

```

```{r}
#Putting it all together

## Q1 What is the difference in average 2023 valuation per SQFT by conversion status?

AvDiff <- lm(log(PerSQFT_2023) ~ Conv_Method, data = Conversions)

summary(AvDiff)

stargazer(AvDiff, type = "latex")

#Intercept for Conv_Method = 1.0385
#exp(1.0385) = 2.824976

#Reuse is associated with ~182% higher valuation than New Construction

## Q2 exact matching ... delta total... how much does change in 2023 valuation per SQFT change based on conversion status
## selecting matching variables: only confounding measurements before Conversion that are associated with both Conversion and PerSQFT2023. 

view(Conversions)

#I would like to match on OfficePerSQFT_2010, because this would try control for whether more valuable properties select into reuse. Issue is that this is continuous. I suppose I could do quartiles? Matching on continuous variables is possible but much more complicated.
M_exact <- matchit(Conv_Method ~ BORO + OfficePerSQFT_2010, data = Affairs, method = "exact", distance = "glm", link = "logit", estimand = "ATT", ratio = 1)

summary(M_exact)

m.data <- match.data(M_exact)

head(m.data) # we can see the 4 subclasses: for each combo of Married & children, and then their corresponding weight

dTot <- lm(Duration ~ Affair, m.data, weights = weights)

print(dTot) # Estimate for dTot

stargazer(dTot, type = "latex")

```

